### 2022-07-12 manuscript.tex
Merge pull request #254 from SORTEE-Github-Hackathon/DrMattG-Abstract_fhillemann [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/1aab55c67fc728559fe52f3f106965c1eef0e179.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/1aab55c67fc728559fe52f3f106965c1eef0e179/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2658244426

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/63f18c11f35a239c2085d7d7dfdb935614f182cf/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/63f18c11f35a239c2085d7d7dfdb935614f182cf}{SORTEE-Github-Hackathon/manuscript@63f18c1}
on July 12, 2022.

@@

Researchers in ecology and evolutionary biology are increasingly dependent on computational code to conduct research.
With the growing role of data science in research, the use of efficient methods to share, reproduce, and collaborate on code has become fundamental.
GitHub is an online, cloud-based service that can help researchers track, organize, discuss, share, and collaborate on software and code.
Despite these benefits, the use of GitHub by EEB researchers is not widespread due to the lack of domain-specific information and guidelines.
To help EEB researchers adopt useful features from GitHub in their own workflows, we review twelve practical ways to use the platform.
We outline features ranging from low to high technical difficulty: storing code, managing projects, coding collaboratively, conducting peer review, and writing a manuscript.
Given that members of a research team may have different technical skills and responsibilities, we describe how the optimal use of GitHub features may vary among members of a research collaboration.
As more ecologists and evolutionary biologists establish their workflows using GitHub, the field can continue to push the boundaries of collaborative, transparent, and open research.

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/1aab55c67fc728559fe52f3f106965c1eef0e179/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/1aab55c67fc728559fe52f3f106965c1eef0e179}{SORTEE-Github-Hackathon/manuscript@1aab55c}
on July 12, 2022.

@@

Researchers in ecology and evolutionary biology are increasingly dependent on computational code to conduct research, and the use of efficient methods to share, reproduce, and collaborate on code as well as any research-related documentation has become fundamental.
GitHub is an online, cloud-based service that can help researchers track, organize, discuss, share, and collaborate on software and other materials related to research production, including data, code for analyses, and protocols.

Despite these benefits, the use of GitHub by EEB researchers is not widespread due to the lack of domain-specific information and guidelines.
To help EEB researchers adopt useful features from GitHub in their own workflows, we review twelve practical ways to use the platform.
We outline features ranging from low to high technical difficulty: storing code, managing projects, coding collaboratively, conducting peer review, and writing a manuscript.
Given that members of a research team may have different technical skills and responsibilities, we describe how the optimal use of GitHub features may vary among members of a research collaboration.
As more ecologists and evolutionary biologists establish their workflows using GitHub, the field can continue to push the boundaries of collaborative, transparent, and open research.
